Open-Set Domain Adaptation through Self-Supervision

### 2022-02-13 paper/main.tex
Updated Images
Updated Captions

To wrap up, our \textbf{main contributions} are: 
\begin{enumerate}
  \item we define a new method to tackle OSDA problems which exploits the rotation recognition task to perform both the known/unknown target separation
and the domain adaptation;
  \item we introduce a new OSDA metric which properly balances the measure of both the performance on predicting the known classes and the performance on doing the unknown rejection;
  \item we conduct an extensive ablation over the hyperparameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
\end{enumerate}

% Classical machine learning in the past years has made some oversimplified assumptions actually detached % Punteggiatura?
% from the usage of artificial intelligence systems in everyday real world and the problems they come with.

% The first assumption is that training and test sets come from the same distributions:
% a model trained on labeled data is expected to perform as well as on the test data.
% However, this assumption not always holds in real-world applications, 
% where naively applying the trained model on a new dataset may cause degradation in the performance.
% To solve this problem Domain Adaptation is widely used, 
% where the goal is to train a neural network on a source dataset for which labels are available and search for good performance on a target dataset, 
% which is related to but significantly different from the source dataset, 
% and whose label or annotation is not available. 
% Generally this is done by by minimizing the difference between domain distributions and enforcing the recognition of domain invariant patterns in both domains. 
% As underlined in \cite{domainAdaptFarahani}, 
% this is usually achieved by mapping source and target data by learning transformations for extracting such features and minimizing the gap between domains in the new representation space in an optimization procedure,
% while preserving the underlying structure of the original data.

% Secondly, 
% in real-world classification tasks it is usually difficult to collect training samples to exhaust all classes when training a model.
% A more realistic scenario is open set recognition (OSR) \cite{OSRsurvey},
% where incomplete knowledge of the world exists at training time and unknown classes can be injected during testing, 
% requiring classifiers to not only accurately classify the seen classes but also effectively deal with unseen ones,
% which would otherwise drastically weaken the robustness of the methods.
% On the contrary this system should reject unknown classes at test time and separate the known and unknown samples.
% As underlined by \cite{OSRclassRec}, 
% existing open-set classifiers rely on deep networks trained in a supervised fashion on known classes in the training set;
% this causes specialization of learned representations to known classes and makes it hard to distinguish the unknowns from the knowns.

% To solve these significant issues our method is focused on a self-supervised task. 
% Self-supervised learning is an unsupervised learning technique where the supervised task is created out of the unlabeled input data. 
% This task could be as simple as predicting the lower half of an image being given the upper half of the same.
% Supervised learning requires both labeled and high quality data,
% usually very expensive, 
% whereas unlabeled data is often readily available in abundance.
% The fundamental idea behind self-supervised learning is creating some auxiliary task from input data so that,
% by solving such task,
% the model can learn the underlying structure of the data,
% for instance high-level knowledge, correlations, and metadata embedded in the data.
% This type of learning was recently used for Domain Adaptation, 
% learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
% and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,dectionGeometric}.

% The approach presented in this paper brings these topics together in the so called Open-Set Domain Adaptation (OSDA) problem. 
% A two-stage method is hence proposed, 
% aiming to identify and isolate unknown class samples in the first stage, 
% before reducing in the second stage the domain gap between the source domain and the known target domain to avoid negative transfer.
% This is done in both stages using a modified version of the rotation task as self-supervised model,
% predicting the relative rotation between an image and its rotated version.
% Finally a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
% being rejected in the latter case.

% The method was evaluated on the Office-Home benchmark \cite{OfficeHomeDataset} with a specific OSDA metric.

% {\bf ADD HERE RESULTS AND A BRIEF OF CONCLUSIVE IDEAS (ALSO POSSIBLE FUTURE WORKS)!!}

%------------------------------------------------------------------------
\section{Related Work}
\label{sec:relatedwork}
\textbf{Closed-Set Domain Adaptation} is the setting where labeled training data is 
available on a source domain, but the goal is to have good performance on a 
unlabeled target domain with a different marginal distribution
of data. The aim is to align the learned representations of the source and target domains.

@@

\begin{figure}
  \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth]{scheme_step1.png}
  \caption{\label{fig:step1} Schema representing the step 1 training}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth ]{scheme.png}
  \caption{\label{fig:separation}\centering Schema representing the target images separation process}
\end{figure}

In this step,
having separated the target into a known part $\mathcal{D}_t^{knw}$,
and an unknown part $\mathcal{D}_t^{unk}$,
we arrange two new datasets in order to perform the domain alignment while also learning
the unknown class.
The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$,
which contains the original source images plus the target images identified as unknown classes.
We thus set the labels for $\mathcal{D}_t^{unk}$ as the class {\it unknown}.
The second one is $\mathcal{D}_t^{knw}$, which can be used to perform the domain alignment
without the risk of negative transfer.
While the feature extractor $E$ is inherited from the previous stage and leverages the previous training phase,
we also use two new classifiers,
$C_2$ and $R_2$.
They are similar to the previous classifiers but they have two important differences.
$C_2$ now has a $(|\mathcal{C}_s|+1)$-dimensional output to accomodate also the unknown class predictions and also
benefits from the previous learning,
while $R_2$ is always a single-head rotation classifier and starts the learning from scratch.
The training phase is the same as before with the difference that we do not have the center loss this time.
We also employ a different hyperparameter $\alpha_2$ to weigh the rotation classifier loss contribution.
The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
We report the $\mathcal{L}_{R_2}$ loss contribution to make clear the usage of $\alpha_2$ and we
recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.

\begin{figure}[ht]
  \includegraphics[trim= 5.2cm 0cm 2cm 0cm, clip, width=\linewidth ]{scheme_step2.png}
  \caption{\label{fig:step2}\centering Test Caption}
\end{figure}

@@

As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
For the feature extraction, we employ a ResNet-18\cite{ResNet18} pre-trained on ImageNet.
All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
with a weight decay of 0.0005 and a momentum of 0.9.
The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
so the training process needs to be speeded up.
Moreover, we set a learning rate 10 times lower for the feature extractor weights.
We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
For models using the center loss a centroid learning rate of 0.001 is used.
The other hyperparameters are analyzed performing an ablation on appendix \ref{sec:tables}.

@@

\subsection{Results}
\label{sec:results}
\begin{figure}[!htb]
  \centering
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
  \end{subfigure}
  \caption{\centering\label{fig:hyperparams} HOS values for different parameters. For full reference see appendix \ref{sec:tables}}
\end{figure}

@@

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

@@

This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyperparameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyperparameters.

\begin{table}[hb!]
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    & {\bf 0.70} & & {\bf 44.38\%} \\
    & 0.75 & & 43.87\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyperparameters picking process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

\begin{table}[t!]
  \vspace{-1.7cm}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{ON-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 43.48\%} \\
    3.0  & & & 38.45\% \\
    5.0  & & & 37.61\% \\
    10.0 & & & 33.23\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.4 & \multirow{6}{*}{3.0}  & 38.40\%\\
    & 0.45 & & 42.40\% \\
    & 0.5 & & 43.48\% \\
    & 0.55 & & 46.21\% \\
    & {\bf0.6} & & {\bf 50.17\%} \\
    & 0.65 & & 45.82\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 46.02\%\\
    && 1.0 & 47.71\% \\
    && 2.0 & 46.56\% \\
    && {\bf 3.0} & {\bf 50.17\%} \\
    && 4.0 & 46.57\% \\
    && 5.0 & 47.52\% \\
    && 10.0 & 44.56\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonoff} Hyperparameters picking process for configuration Multi-Head On and Center-Loss Off}
\end{table}

\begin{table}[hb!]
  \centering
  \begin{tabular}[h]{||c|c|c|c||c||}
    \hline
    \multicolumn{5}{||c||}{ON-ON} \\
    \hline
    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.01} & \multirow{4}{*}{0.05} & \multirow{4}{*}{3.0} & 44.90\% \\
    {\bf 3.0} & && & {\bf 45.33\%} \\
    5.0 & && & 42.41\% \\
    10.0 & && & 37.15\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
    \hline
    \multirow{5}{*}{3} & 0.0001 & \multirow{5}{*}{0.5} & \multirow{5}{*}{3.0} & 39.90\% \\
    & 0.001 & & & 36.71\% \\
    & 0.01 & & & 45.33\% \\
    & {\bf 0.05 }& & & {\bf 46.63\%} \\
    & 0.1 & & & 37.44\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{5}{*}{3} & \multirow{5}{*}{0.05} & 0.4 & \multirow{5}{*}{3.0} & 44.32\% \\
    & & 0.45 & & 45.13\% \\
    & & 0.5 & & 46.63\% \\
    & & 0.55 & & 47.09\% \\
    & & {\bf 0.6} & & {\bf 49.78\%} \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{3} & \multirow{7}{*}{0.05} & \multirow{7}{*}{0.6} & 0.1 & 45.73\% \\
    & & & 1.0 & 45.23\% \\
    & & & 2.0 & 45.76\% \\
    & & & {\bf 3.0} & {\bf 49.78\%} \\
    & & & 4.0 & 46.20\% \\
    & & & 5.0 & 48.60\% \\
    & & & 10.0 & 44.14\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonon} Hyperparameters picking process for configuration Multi-Head On and Center-Loss On}
\end{table}

\begin{table*}
  \centering
  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
    \hline
    \multicolumn{13}{||c||}{Results} \\
    \hline
    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
    \hline
    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
    A$\to$R & 27.94 & 68.13 & 17.58 & 52.25 & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & 58.64 & 46.81 & 60.95 & 37.99 \\
    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
    \hline
    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 52.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Results for each configuration and each domain shift. All values are percentages.}
\end{table*}

>>>>

To wrap up, our \textbf{main contributions} are: 
\begin{enumerate}
  \item we define a new method to tackle OSDA problems which exploits the rotation recognition task to perform both the known/unknown target separation
and the domain adaptation;
  \item we introduce a new OSDA metric which properly balances the measure of both the performance on predicting the known classes and the performance on doing the unknown rejection;
  \item we conduct an extensive ablation over the hyper-parameters for different variants of the self-supervised task underlying the benefits of some techniques over others.
\end{enumerate}

\section{Related Work}
\label{sec:relatedwork}
\textbf{Closed-Set Domain Adaptation} is the setting where labeled training data is 
available on a source domain, but the goal is to have good performance on a 
unlabeled target domain with a different marginal distribution
of data. The aim is to align the learned representations of the source and target domains.

@@

\begin{figure}
  \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth]{scheme_step1.png}
  \caption{\label{fig:step1} Schema of the learning process for the model in Step I.}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[trim= 0cm 0cm 0cm 0cm, clip, width=\linewidth ]{scheme.png}
  \caption{\label{fig:separation}\centering Schema of the separation process into known and unkown samples on target images}
\end{figure}

In this step,
having separated the target into a known part $\mathcal{D}_t^{knw}$,
and an unknown part $\mathcal{D}_t^{unk}$,
we arrange two new datasets in order to perform the domain alignment while also learning
the unknown class.
The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$,
which contains the original source images plus the target images identified as unknown classes.
We thus set the labels for $\mathcal{D}_t^{unk}$ as the class {\it unknown}.
The second one is $\mathcal{D}_t^{knw}$, which can be used to perform the domain alignment
without the risk of negative transfer.
While the feature extractor $E$ is inherited from the previous stage and leverages the previous training phase,
we also use two new classifiers,
$C_2$ and $R_2$.
They are similar to the previous classifiers but they have two important differences.
$C_2$ now has a $(|\mathcal{C}_s|+1)$-dimensional output to accomodate also the unknown class predictions and also
benefits from the previous learning,
while $R_2$ is always a single-head rotation classifier and starts the learning from scratch.
The training phase is the same as before with the difference that we do not have the center loss this time.
We also employ a different hyper-parameter $\alpha_2$ to weigh the rotation classifier loss contribution.
The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
We report the $\mathcal{L}_{R_2}$ loss contribution to make clear the usage of $\alpha_2$ and we
recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.

\begin{figure}[ht]
  \includegraphics[trim= 5.2cm 0cm 2cm 0cm, clip, width=\linewidth ]{scheme_step2.png}
  \caption{\label{fig:step2}\centering Schema of the learning process of the model in Step II}
\end{figure}

@@

As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
For the feature extraction, we employ a ResNet-18\cite{ResNet18} pre-trained on ImageNet.
All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
with a weight decay of 0.0005 and a momentum of 0.9.
The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
so the training process needs to be speeded up.
Moreover, we set a learning rate 10 times lower for the feature extractor weights.
We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
For models using the center loss a centroid learning rate of 0.001 is used.
The other hyper-parameters are analyzed performing an ablation on appendix \ref{sec:tables}.

@@

\subsection{Results}
\label{sec:results}
\begin{figure}[!htb]
  \centering
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
  \end{subfigure}
  \caption{\centering\label{fig:hyperparams} HOS values for different hyper-parameters. For full details see appendix \ref{sec:tables}}
\end{figure}

@@

%%%%%%%%% REFERENCES
{\small
\nocite{BucciROS}
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

@@

This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyper-parameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyper-parameters.

\begin{table}[hb!]
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    & {\bf 0.70} & & {\bf 44.38\%} \\
    & 0.75 & & 43.87\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyper-parametr optimization process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

\begin{table}[t!]
  \vspace{-1.7cm}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{ON-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 43.48\%} \\
    3.0  & & & 38.45\% \\
    5.0  & & & 37.61\% \\
    10.0 & & & 33.23\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.4 & \multirow{6}{*}{3.0}  & 38.40\%\\
    & 0.45 & & 42.40\% \\
    & 0.5 & & 43.48\% \\
    & 0.55 & & 46.21\% \\
    & {\bf0.6} & & {\bf 50.17\%} \\
    & 0.65 & & 45.82\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 46.02\%\\
    && 1.0 & 47.71\% \\
    && 2.0 & 46.56\% \\
    && {\bf 3.0} & {\bf 50.17\%} \\
    && 4.0 & 46.57\% \\
    && 5.0 & 47.52\% \\
    && 10.0 & 44.56\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonoff} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss Off}
\end{table}

\begin{table}[hb!]
  \centering
  \begin{tabular}[h]{||c|c|c|c||c||}
    \hline
    \multicolumn{5}{||c||}{ON-ON} \\
    \hline
    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.01} & \multirow{4}{*}{0.05} & \multirow{4}{*}{3.0} & 44.90\% \\
    {\bf 3.0} & && & {\bf 45.33\%} \\
    5.0 & && & 42.41\% \\
    10.0 & && & 37.15\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
    \hline
    \multirow{5}{*}{3} & 0.0001 & \multirow{5}{*}{0.5} & \multirow{5}{*}{3.0} & 39.90\% \\
    & 0.001 & & & 36.71\% \\
    & 0.01 & & & 45.33\% \\
    & {\bf 0.05 }& & & {\bf 46.63\%} \\
    & 0.1 & & & 37.44\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{5}{*}{3} & \multirow{5}{*}{0.05} & 0.4 & \multirow{5}{*}{3.0} & 44.32\% \\
    & & 0.45 & & 45.13\% \\
    & & 0.5 & & 46.63\% \\
    & & 0.55 & & 47.09\% \\
    & & {\bf 0.6} & & {\bf 49.78\%} \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{3} & \multirow{7}{*}{0.05} & \multirow{7}{*}{0.6} & 0.1 & 45.73\% \\
    & & & 1.0 & 45.23\% \\
    & & & 2.0 & 45.76\% \\
    & & & {\bf 3.0} & {\bf 49.78\%} \\
    & & & 4.0 & 46.20\% \\
    & & & 5.0 & 48.60\% \\
    & & & 10.0 & 44.14\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonon} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss On}
\end{table}

\begin{table*}
  \centering
  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
    \hline
    \multicolumn{13}{||c||}{Results} \\
    \hline
    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
    \hline
    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
    A$\to$R & 27.94 & 68.13 & 17.58 & 52.25 & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & 58.64 & 46.81 & 60.95 & 37.99 \\
    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
    \hline
    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 52.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Final results for the three configurations on all domain shifts. All values are percentages.}
\end{table*}
